---
title: "Day 10 Practice"
output: html_document
---

Let's try to simulate the impact of the "file drawer" problem on effect-size estimates.

#### 1. First, simulate data with 100 observations of two variables that are correlated at .3.
```{r}
simulate
require(MASS)

set.seed(50)
cor.data <- mvrnorm(n = 100, mu = c(0, 0), Sigma = matrix(c(1, .3, .3, 1), nrow = 2),empirical=T)
cor.data <- as.data.frame(cor.data)
head(cor.data)
```

#### 2. Run a cor.test and get a p-value.

```{r}
results1 <- cor.test(cor.data$V1,cor.data$V2)
#Correlation
results1$estimate
#p-value
results1$p.value
```

#### 3. Now run simulations with very low power (like 10 or 20 observations).  For each simulation, record both the correlation and the p-value of the cor.test.

```{r}
sim1 <- function(n=10){
  cor.data2 <- mvrnorm(n, mu = c(0, 0), Sigma = matrix(c(1, .3, .3, 1), nrow = 2))
  cor.data2 <- as.data.frame(cor.data2)
  cor <- cor.test(cor.data2$V1,cor.data2$V2)
  results <- data.frame("cor" = cor$estimate,"p-value" = cor$p.value,row.names=NULL)
  results
}
system.time(sims <- replicate(100, sim1(10)))
sim.output <- data.frame(sims)

### or another method
nsim <- 1000

results.table <- data.frame(cor=rep(NA,nsim),pval=NA)

for(i in 1:nsim){
  simdata <- mvrnorm(n, mu = c(0, 0), Sigma = matrix(c(1, .3, .3, 1), nrow = 2),empirical = F)
  simcor.test <- cor.test(simdata[,1],simdata[,2])
  simcor <- simcor.test$estimate
  pval <- simcor.test$p.value
  results.table[i,] <- c(simcor,pval)
}

```


#### 4. Check to see what the distribution of correlations are, only for the runs where p < .05.

```{r}
alpha <- .05
library(dplyr)
library(ggplot)
results.sig <- filter(results.table, pval < alpha)
ggplot(results.table,aes(cor)) + geom_histogram()
ggplot(results.table,aes(pval)) + geom_histogram()
```

