---
title: "Day 9 Practice"
output: html_document
---

1. Use the following data:

```{r}
myiris <- iris
set.seed(42)
for(col in 1:4) {
  myiris[sample(nrow(myiris), 20, replace = FALSE), col] <- NA
} #Creating NAs 
```

2. Write a function that will:
  - take a vector of numbers as input
  - return the log of the largest non-NA value
  - Try this out on a vector that you make up
  
```{r}
#First, just making the code work once.
vec <- seq(1,20,3)
vec
lnvec <- log(max(vec))
lnvec

my.func <- function(x){
  lnvec <- log(max(x))
  lnvec
}
my.func(4:500)
#Good. But what if there are NAs?

vec2 <- c(1:5,NA,8)
vec2
my.func(vec2) #Returns NA

#trouble shooting
my.func <- function(x){
  lnvec <- log(max(x))
  if(is.na(lnvec)){
    stop("Remove NA values from vector.")
    }
  lnvec
}
my.func(vec2)
my.func(4:50)
#Good.
```

3. Run this function over rows of the data from #1

```{r}
myiris$newcol <- apply(myiris[,1:4],1,my.func)
head(myiris) #good
```

4. Write a function that will get the standard error of a vector of numbers. Use that function to get a standard error for each measure for each Species in the data from #1 (ignoring NAs)

If I remember correctly, the equation for sample variance is

sum(x-mean)^2/n

Making the sample Standard Deviation (or Standard Error) == sqrt(sum((x-sample.mean)^2)/n) == s/sqrt(n)

```{r}
require(dplyr)

#Here essentially is the process that we need
diff.squ <- NA
for(i in 1:10){ 
  mean <- mean(1:10)
  diff.squ[i] <- (i-mean)^2
  }
  sum.squ <- sum(diff.squ)
  n <- length(1:10)
  Std.Err <- sqrt(sum.squ/n)

#Applying the above to a species subset from iris data
sub <- myiris %>%  filter(Species=="setosa")#Creating Subset

diff.squ <- NA
attach(sub)
for(i in 1:nrow(sub)){
  if(is.na(Petal.Length[i])){
    next
    } else{
      mean <- mean(!is.na(Petal.Length))
      diff.squ[i] <- (Petal.Length[i]-mean)^2 
    }
  }
sum.squ <- sum(!is.na(diff.squ))
n <- nrow(sub)
Std.Err <- sqrt(sum.squ/n)
detach(sub)

#Now I need to package it into a more generic framework to work as a function.

std.err <- function(variable){
  diff.squ <- NA
  for(i in 1:length(variable)){
    if(is.na(variable[i])){
      next
      } else{
        mean <- mean(!is.na(variable))
        diff.squ[i] <- (variable[i]-mean)^2 
        }
    } 
  sum.squ <- sum(!is.na(diff.squ))
  s <- sqrt(sum.squ)
  n <- length(variable) 
  Std.Err <- s/sqrt(n) 
  Std.Err
  }
std.err(myiris$Petal.Length)
#Not the best function in the world...but it does the job for now. 

####________________________________________#####
#Here is a less convoluted way to do the same thing would be
std <- function(x) sd(!is.na(x))/sqrt(length(x))
std(myiris$Petal.Length)
#hmmm....this returns a different result...so which is wrong.

#I need a third opinion
library(plotrix)
std.error(myiris$Petal.Length)
#offers even a different value...hmm maybe the issue is with the NAs

##### Comparing via tweeking the function
std <- function(x){
  x <- x[!is.na(x)] #This will drop the NAs
  sd(x)/sqrt(length(x))
  }
std(myiris$Petal.Length)
#That's it...they are dropping the NAs in the
#plotrix version of the function. 

myiris.Std.err <- apply(myiris[1:4],2,std)
myiris.Std.err 
```

So given the above computation...the question is which was is correct? Should one drop the NAs or account for them when computing the N?


