---
title: "Duration Counter"
output: html_document
---
Duration (or count) variables are used in event history data to count the number of instances since an event occurred. The data typically looks like this:

```{r}
df <- data.frame("year"=c(1991:2000),"event"=c(0,0,1,0,0,0,0,0,1,0))
df
```

Here the event is dichotomously coded. The duration counter works as follows:
```{r}
df1 <- data.frame("year"=c(1991:2000),"event"=c(0,0,1,0,0,0,0,0,1,0),"duration"=c(2,3,0,1,2,3,4,5,0,1))
df1
```

The goal is to create the duration counter.

### Creating the Counter

```{r}
#Using Fake Data
df
for(i in 1:nrow(df)){
  if(df$event[i]==1){
    df$counter[i] <- 0 
    } else{ if(!i==1){
      df$counter[i] <- df$counter[i-1] + 1
      } else{df$counter[i] <- 1}
      }
  }
df
```

The counter is successful, but this is relatively simple array of dates. Now I need to expand it to work around different forms of grouping. 

### Handling groups

```{r}
#Again, using fake data, but this time adding groupings.
df2 <- data.frame("group"=c(rep("Group_A",5),rep("Group_B",5)), "year"=c(1991:1995,1999:2003),"event"=c(0,0,1,0,0,0,0,0,1,0))
df2

#counter
require(dplyr)
no.groups <- as.character(unique(df2$group))
for(j in 1:length(no.groups)){
  temp <- df2 %>% filter(group==no.groups[j]) 
  for(i in 1:nrow(temp)){
    if(temp$event[i]==1){
      temp$counter[i] <- 0 
      } else{ if(!i==1){
        temp$counter[i] <- temp$counter[i-1] + 1
        } else{temp$counter[i] <- 1}
        }
    }
  output <- rbind(output,temp)
  temp <- NA
  }
output 
```


### Event History - Cubic Polynomial Function
Following with the method outlined in Carter and Sigorino to deal with temporal dependence in event history data. The following will create the t, $t^2$, and $t^3$ necessary for the cubic polynomial approach. 

```{r}
#Another fake dataset
df3 <- data.frame("group"=c(rep("Group_A",10),rep("Group_B",10),rep("Group_C",7)), 
                  "year"=c(1991:2000,1999:2008,1945:1951),
                  "event"=c(c(0,0,1,0,0,0,0,0,1,0),
                  c(1,0,1,1,0,0,0,0,0,0),c(0,0,0,0,0,0,1)))


csEvent <- function(data,date.var,event.var,grouping.var){
  require(dplyr)
  output <- NULL
  #temp <- data.frame
  no.of.groups <- as.character(unique(data[,grouping.var]))
  for(j in 1:length(no.of.groups)){
    temp <- filter(data,as.character(data[,grouping.var])==no.of.groups[j])
    temp <- arrange(temp,temp[,date.var])
    for(i in 1:nrow(temp)){
      if(temp[,event.var][i]==1 & !is.na(temp[,event.var][i])){
        temp$t[i] <- 0 
        } else{ if(!i==1){
          temp$t[i] <- temp$t[i-1] + 1
          } else{temp$t[i] <- 1}
          }
      }
    output <- rbind(output,temp)
    temp <- NA
    }
  output$t2 <- output$t^2
  output$t3 <- output$t^3
  return(output)
  }

#Test the function
csEvent(df2,"year","event","group")
csEvent(df3,"year","event","group")
```

The function works for the fake data that we used to build the function, but now, I will test to see if it holds up when applied to real dataset. 

For the test, I will use a working dataset that I am putting together for Birnir. "rebellion" is an indicator variable for whether there was a rebellion or not for that group country year. "ID" is a unique identifier for country-ethnic group.
```{r}
#Importing data
amar.data <- read.csv("Data/Mobil.Data.Final.csv")
amar.data <- amar.data %>% select(country:ID,polity2,rebellion)
head(amar.data) 

csEvent(amar.data,"year","rebellion","ID") %>% head(20)
```

The function works, though there are larger issues with the data (i.e. the ID variable is sometimes redundant for a year, the time like is not always consecutive, etc.). Future iterations of the function needs to take into account the years and whether or not they are consecutive. 

