---
title: "Day 10 Homework"
author: "Eric Dunford"
output: html_document
---
```{r}
#Data
data <- read.csv("Data/NAVCO_2.0.csv") 
#Packages
require(dplyr)
require(MASS)
require(ggplot2)
require(RColorBrewer)
```

#### 1. Find some relationship in your data (e.g., correlation, comparison of means, etc.) that is "significant" (don't worry too much about what that might mean).

Looking at a simple bivariate relationship between a movements decision to provide social services and its effect on the the movement's progress toward its stated goals.
```{r}
summary(data$progress)
summary(data$pi_socwel)
results <- summary(lm(progress~pi_socwel,data=data)) #OLS - note appropriate given the variables
results
```

#### 2. Get an estimate of the effect size (e.g., the difference between means, or the correlation).

Let's just look at how these two variables correlate.
```{r}
corr <- cor.test(data$progress,data$pi_socwel)
corr$estimate #Effect
corr$p.value #p-value
corr$parameter #Degress of Freedom
```

Movements that provide good and services for their constituencies are on average less successful in achieving their stated goals.

#### 3. Simulate data with this effect size (either using mvrnorm or adding a simulated effect), but with a much smaller data sample.  In other words, simulate an underpowered study.

```{r}
#means and var-cov same as original data.
#Looping method
sims <- 1000
results.table <- data.frame(cor=NA,pval=NA,sim_num = 1:sims)
for(i in 1:sims){
  sim.data <- mvrnorm(100,mu=c(0.7604,0.4568),Sigma=matrix(c(1,-0.1003577,-0.1003577,1),nrow=2)) %>% as.data.frame(.)
  sim.corr <- cor.test(sim.data$V1,sim.data$V2)
  results.table[i,1] <- sim.corr$estimate
  results.table[i,2] <- sim.corr$p.value
}
summary(results.table)
```


#### 4. Examine the amount of effect-size inflation via the "significance filter" by looking at the effect sizes from the simulations, for just the sims where the effect turned out significant.

```{r}
alpha <- .05
sim.effect <- filter(results.table,pval < alpha)
ggplot(sim.effect,aes(x=cor)) + geom_histogram() + theme_bw() 

#I think this is what the question is asking (similar to the practice)
results.table$stat.sig <- results.table$pval < alpha
effect.plot <- ggplot(results.table, aes(x=cor)) + geom_histogram(aes(fill = stat.sig)) + 
  geom_vline(xintercept = -0.1003577, linetype = 2) + theme_bw()
effect.plot

effect.plot.faceted <- ggplot(results.table, aes(x=cor)) + geom_histogram(aes(fill = stat.sig)) + 
  geom_vline(xintercept = -0.1003577, linetype = 2) + theme_bw() + facet_grid(stat.sig ~ .)
effect.plot.faceted
```

This is interesting. All the statistically significant results are substantively off. If the true population correlation was -.1 as it is in the data, then if we only sought out statistical significance given a low number of observations, we'd be reporting biased results... or something along those lines. Interesting! And cool way to go about thinking through this. 

----

Let's do the same thing but this time running the simulation with the exact same number of observations as in the data...will the results be generally the same?

```{r}
sims <- 1000
results.table2 <- data.frame(cor=NA,pval=NA,sim_num = 1:sims)
for(i in 1:sims){
  sim.data <- mvrnorm(1305,mu=c(0.7604,0.4568),Sigma=matrix(c(1,-0.1003577,-0.1003577,1),nrow=2)) %>% as.data.frame(.)
  sim.corr <- cor.test(sim.data$V1,sim.data$V2)
  results.table2[i,1] <- sim.corr$estimate
  results.table2[i,2] <- sim.corr$p.value
}
summary(results.table2)
results.table2$stat.sig <- results.table2$pval < alpha
effect.plot.faceted2 <- ggplot(results.table2, aes(x=cor)) + geom_histogram(aes(fill = stat.sig)) + 
  geom_vline(xintercept = -0.1003577, linetype = 2) + theme_bw() + facet_grid(stat.sig ~ .)
effect.plot.faceted2
```

Neat!
