---
title: "Day 3 Homework"
author: Eric Dunford - PSYC 789W - Winter 2015
output: html_document
---
Date: `r Sys.Date()`

```{r, echo=F}
#Read data in.
setwd("~/Dropbox/Coursework/Winter 2015/PSYC798W -R_Programming")
data <- read.csv("Data/NAVCO_2.0.csv") 
```

The goal of this homework is to get practice with manipulating data.^[Note that the data used here is consistent with what I sent you for Day2 HM.]

#### 1. Make both a "wide" and a "long" version of your data

First, given the number of variables in my data, I will create a subset of relevant variables. 

```{r}
sub <- data[,c("year","campaign","location","camp_size","pi_newmedia","pi_tradmedia","camp_support","ingo_support","prim_method")]
head(sub)
```

The data is already in a 'wide' form. Let's melt it into a *long*er format. 

```{r}
require(reshape2)
sub.melt <- melt(sub,id.vars = c("campaign","location","year"), measure.vars = c("camp_size","pi_newmedia","pi_tradmedia","camp_support","ingo_support","prim_method"))
head(sub.melt)
```

For the sake of the exercise, I will now cast the data back into its original form.

```{r}
sub.cast <- dcast(sub.melt, campaign+location+year~variable,value.var = "value")
head(sub.cast) #looks good
```

#### 2. Transform a variable

Let's transform the `camp_size` variable into a factor.

Pulling from a quote in the NAVCO 2.0 Codebook for the `camp_size` variable.

>0=1-999 1=1000-9,999 2=10,000-99,999 3=100,000-499,999 4=500,000-1million 5=>1 million -99=unknown

```{r}
sub$camp_size2 <- ifelse(sub$camp_size==0,"1-999",
                         ifelse(sub$camp_size==1,"1000-9,999",
                                ifelse(sub$camp_size==2,"10,000-99,999",
                                       ifelse(sub$camp_size==3,"100,000-499,999",
                                              ifelse(sub$camp_size==4,"500,000-1 million",
                                                     ifelse(sub$camp_size==5,"1 million +",NA))))))
table(sub$camp_size)
table(sub$camp_size2)
```

The change when through but the order of the characters are odd. Let's convert the variable to a factor to set the data for question 3.

```{r}
class(sub$camp_size2)
sub$camp_size2 <- as.factor(sub$camp_size2)
class(sub$camp_size2)
```


#### 3. Recode a factor

Interpreting "recode" as "reorder"...

```{r}
levels(sub$camp_size2)
sub$camp_size2 <- factor(sub$camp_size2,levels(sub$camp_size2)[c(2,5,3,4,6,1)])
levels(sub$camp_size2)
```


#### 4. Add a new factor, where the levels are conditional on the values of some other variable. E.g., a factor of "high", "medium", and "low" based on thresholds for another variable.

Let's create a time period variable, capturing the following:

* Cold War Period (1945-1989)
* Post Cold War Period (1990 - 2001)
* Post 9/11 Period (2002 - 2006^[This is when the data set ends.])

```{r}
sub$timePeriod <- ifelse(sub$year>=1945 & sub$year<=1989,"Cold War Period",
                         ifelse(sub$year>=1990 & sub$year<=2001,"Post Cold War Period",
                                ifelse(sub$year>=2002,"Post 9/11 Period",NA)))
table(sub$timePeriod)
class(sub$timePeriod)
#following with the question
sub$timePeriod <- as.factor(sub$timePeriod)
class(sub$timePeriod)
```

#### 5. Reorder the levels of this new factor

```{r}
levels(sub$timePeriod)
```

Let's reorder it so that the periods are chronological.

```{r}
sub$timePeriod <- factor(sub$timePeriod,levels=c("Cold War Period","Post Cold War Period","Post 9/11 Period"))
levels(sub$timePeriod)
```

#### 6. Choose a factor that could be re-coded as multiple dimensions (recall the sepal/petal vs. length/width breakdown). If you don't have one, try to create one.  Now create two (or more) new factors that represent these dimensions.

There isn't really a great variable on hand within the subset to really do what the question is asking for. In addition to this, I tried playing around with ways of generating fake variables that never really panned out.

#### 7. Using `dcast`, aggregate some variable into "cell means" of some kind.

Using the `sub.melt` object I generated above

```{r}
sub.cast2 <- dcast(sub.melt, campaign~variable,mean)
head(sub.cast2)
```

#### 8.  Save all of the above in a well-documented R Markdown document.  Email me the .Rmd file (and if you use different or updated data from Day 2 Homework, send that to me, too).
