---
title: "Day 6 Homework"
author: Eric Dunford - PSYC 789W
output: html_document
---
```{r,echo=F,message=FALSE}
#Data
setwd("~/Dropbox/Coursework/Winter 2015/PSYC798W -R_Programming")
data <- read.csv("Data/NAVCO_2.0.csv")

#packages
library(plyr)
```

#### 1. Think carefully about your data.  Think about something you would like to do multiple times, to subsets of your data.  

It would be convenient to have a "duration" variable that captures the number of years that a movement lasted for (i.e. if a movement occured from 1992 to 1995, some variable that noted that the campaign lasted 4 years). 

That said, since the data is time series, it might be better to have a counter variable that marks how long the movement has been in teh dataset (if 1992 as the first year in the DF then the counter == 0, 1993 == 1, 1994 == 2; 1995 == 3)

#### 2. Write out (in plain English, in the notebook) what you are trying to do

For the first year that _this movement_ enters the DF, start counting. For each additional year, add one. Stop counting when the movement exits the data frame. 

#### 3. Write some "pseudo-code" comments in an R chunk, as an outline

#### 4. Write some (real) code that will do what you want ONCE, on one subset of the data.

```{r}
#First, arrange the data so the years are in order
data <- arrange(data,data$year); data <- arrange(data,data$campaign)

data.sub <- data[data$campaign=="UNITA",] 
years <- data[data$campaign=="UNITA","year"] 
min.year <- min(years)
duration <- years - min.year
duration #Bingo
```

#### 5. Copy that code chunk, and convert it into a loop, which will do what you want over all the groups, concatenating the results.

```{r}
campaigns <- data$campaign #Vector of all the campaigns
data$duration <- NA #container

for(i in 1:length(campaigns)){
  years <- data[data$campaign==campaigns[i],"year"] 
  min.year <- min(years)
  data$duration[data$campaign==campaigns[i]] <- years - min.year
}
head(data[data$campaign=="UNITA",c("year","duration")],10) # Great!
```


#### 6. Copy that loop again, and at a condition (`if`) statement to add some further control about ignoring some groups or some other conditional operation.
```{r}

for(i in 1:length(campaigns)){
  years <- data[data$campaign==campaigns[i],"year"] 
  min.year <- min(years)
  if(min.year >= 1980){ #Here is the conditional only capturing movements that emerged from 1980 onward
  data$duration[data$campaign==campaigns[i]] <- years - min.year
  } else data$duration[data$campaign==campaigns[i]] <- NA
}
head(data[data$campaign=="Active Forces",c("campaign","year","duration")],3) #This Movement started in 1991 
head(data[data$campaign=="Afghan Resistance",c("campaign","year","duration")],3) #This one in 1979 
#Success!
```


