---
title: "Geo-Location Scraper"
output: html_document
---

The goal here is to build a function where the input is a country name and the output is data frame containing the name of every town in that country and it's longitude and latitude location (geo-code) for maping purposes. The function will require multiple web scrappers: one pulling from Google maps, the other from Wikipedia. The goal of this is to create an easy data frame of geo-codes on demand. Further extensions of this project will also attempt to include ethnicities in the output so that by entering a simple country name, the research is returned with the geographical location of all the towns match with all ethnic groups that (purportedly) live in those locations. 

Below I will construct this function piecemeal, and then include the final result toward the end. 

### Wikipedia Scrapper - Town names. 

```{r}
require(rjson)
require(RCurl)
require(RJSONIO)
url <- "https://github.com/David-Haim/CountriesToCitiesJSON/blob/master/countriesToCities.json"
data <- getURL(url)
data <- rjson::fromJSON(url)

data <- read.table("/Users/edunford/Desktop/ad.txt",header=T,sep=",",fill = T)
fileName <- '/Users/edunford/Desktop/worldcitiespop.txt'
readChar(fileName,nchars=100)
```

#### Twitter API

```{r}

```{r}
fqlQuery='select share_count,like_count,comment_count, comment_content from link_stat where url="'
url="http://www.theguardian.com/world/2014/mar/03/ukraine-navy-officers-defect-russian-crimea-berezovsky"
queryUrl = paste0('http://graph.facebook.com/fql?q=',fqlQuery,url,'"')  #ignoring the callback part
lookUp <- URLencode(queryUrl) #What do you think this does?
lookUp
require(rjson)
rd <- readLines(lookUp, warn="F") 
dat <- fromJSON(rd)
dat
```




Now putting this to use.
```{r}
require(RJSONIO)
getUrl <- function(address,sensor = "false") {
 root <- "http://maps.google.com/maps/api/geocode/json?"
 u <- paste0(root,"address=", address, "&sensor=false")
 return(URLencode(u))
}
getUrl("Kremlin, Moscow")


target <- getUrl("Accra,Ghana")
dat <- fromJSON(target)
latitude <- dat$results[[1]]$geometry$location["lat"]
longitude <- dat$results[[1]]$geometry$location["lng"]
place <- dat$results[[1]]$formatted_address
latitude;longitude;place
```



