---
title: "Utilizing Python and R together"
output: html_document
---

This is an initial look into using Python and R languages together. Python offers strong langauge processing, where as R is easier to control, offers and eclectic and powerful range of programs, and is in general, more utilizable as a social data scientist.

See [here](http://cran.r-project.org/web/packages/rPython/rPython.pdf) for the specifics on the `rPython` package.
```{r}
install.packages("rPython")
require(rPython)

#Application
a <- 1:4
python.assign( "a", a ) 
python.exec( "b = len( a )" )
python.get( "b" )

#to execute a Python script from R
python.load()
```

#### Test one 
Here is a simple python script that I put together and saved into this working directory. Here I will run it and then call it into R. 
```{r}
python.load("R_Py/test1.py")
test1 <- python.get("the_goods") #Here is the basic data
test2 <- python.get("string_1") #Here is a string
x <- python.call("fun_1",10) 

#can we build an R compliant function from this?
fun_1 <- function(x){
  output = python.call("fun_1",x)
  return(output)
}
fun_1(56) #beautiful


#Created a simple dictionary in python...now passing it over
python.load("R_Py/test2.py")
test3 <- python.get("my_dict")
test3
str(test3)
```

