---
title: "FM_Scrape - Processing Data"
output: html_document
---
```{r}
#Relevant packages
require(tm)
require(lubridate)
require(dplyr)
```

The initial scrape using the Russian President's Foreign Ministry news releases was a success. The follwing corpus was created, which effectively archives all this material for future use.^[Note: to read in the corpus file, the `tm` package needs to be loaded, else R will read it in as a different file type.]

```{r}
#Loading RU_Pres corpus
load("RU_Pres_corpus_02.17.15_total.no:2600.Rdata")
```

### Processing the data 
Here we need to synthesize the raw scape materials (i.e. the corpus) into a working (and statistically utilizable) dataframe. There are two ways to proceed:

1. The NLP approach
    + The NLP approach is outlined below; however, it isn't the most effective method (for now), given that the English language processors have trouble isolating the relevate names, date, places, and organizations. There has been considerable progress made in improving this technology, but as for now, the promise of NLP is still out of reach, at least within the context of this analysis. 
    
2. the dictionary approach (which involves creating a dictionary of leader names and position in order extract the names and populated it with the leaders relative status).
    + utilizing text correlations to isolate relevant ties. 

#### Natural Language Processing Approach
```{r, eval=F}
#Here we NL processing programs 
require(rJava)
require(NLP)
require(openNLP)
require(openNLPmodels.en) #English dictionary
# Corpus object meta data
corpus[[170]]$meta

#Using languae processing to extract key information from corpus text
story <- as.String(corpus[[2]]$content) #body text
brief <- as.String(corpus[[2]]$meta[[3]]) # brief

#annotators
word_ann <- Maxent_Word_Token_Annotator()
sent_ann <- Maxent_Sent_Token_Annotator()
person_ann <- Maxent_Entity_Annotator(kind = "person",model="nl-ner-person.bin")
location_ann <- Maxent_Entity_Annotator(kind = "location")
organization_ann <- Maxent_Entity_Annotator(kind = "organization")

#streamline the annotators
pipeline <- list(sent_ann,
                 word_ann,
                 person_ann,
                 location_ann,
                 organization_ann)

#Two "paths":
  #story content
      story_annotations <- annotate(story,pipeline)
      story_doc <- AnnotatedPlainTextDocument(story, story_annotations)
  #brief content
      brief_annotations <- annotate(brief,pipeline)
      brief_doc <- AnnotatedPlainTextDocument(brief, story_annotations)

# Extract entities from Annotation
# Use this borrowed function
entities <- function(doc, kind) {
  s <- doc$content
  a <- annotations(doc)[[1]]
  if(hasArg(kind)) {
    k <- sapply(a$features, `[[`, "kind")
    s[a[k == kind]]
  } else {
    s[a[a$type == "entity"]]
  }
}


#We can in theory extract the relavent names.
#from story
  entities(story_doc,kind = "person") %>% unique #failed
  entities(story_doc,kind = "location") %>% unique #success
  entities(story_doc,kind = "organization") %>% unique #success
#from brief
  entities(brief_doc,kind = "person") %>% unique #failed
  entities(brief_doc,kind = "location") %>% unique #failed
  entities(brief_doc,kind = "organization") %>% unique #failed
````
The natural language processing is still limited in the types of information that it can extract. Primarily, the issue with with non-English names and locations (i.e. any name that doesn't come from a Anglo-traditional work from appears to be missed). This presents real problems for processing information about world leaders (many of which do not have English-based names).

#### Dictionary Approach

```{r}
#Pulling out leader names
#Using the world leader dictionary created above
leader.data <- read.csv('Data/CIA_World_Leaders_Data_01.28.15.csv')
head(leader.data) 

#lowercasing the leader names
leader.data$office.holder <- tolower(leader.data$office.holder)

#Subset of Target country leaders
  rus.leaders <- leader.data %>% filter(country=="Russia")
  rus.leaders$office.holder <- str_trim(rus.leaders$office.holder)
#Subet of all non-target country leaders
  other.leaders <- leader.data %>% filter(!country=="Russia")
  other.leaders$office.holder <- str_trim(other.leaders$office.holder) %>% tolower

#extraction will occur along two paths: the brief and the story content.
#here I will do the briefs since it is more straight forward however 
#the code can be easily manipulated to utilize the larger content of the story
  descr <- corpus[[3]]$meta[[3]] %>% as.character #brief
  descr <- tolower(descr) 
  descr <- descr %>%  strsplit(.," ") %>% .[[1]]
#extracting corpus content; to character
  content <- tm_map(corpus, content_transformer(tolower)) %>%  .[1] %>% inspect
  content <- content[[1]]$content %>% as.character #actual content of the story

#placeholder object
s <- descr 

#Breakup names
  #Target country
  for(i in 1:nrow(rus.leaders)) {
    if(length(strsplit(rus.leaders$office.holder[i]," ")[[1]])==3){
      rus.leaders$last.name[i] <- strsplit(rus.leaders$office.holder[i]," ")[[1]][3]
      rus.leaders$middle.name[i] <- strsplit(rus.leaders$office.holder[i]," ")[[1]][2]
      rus.leaders$first.name[i] <- strsplit(rus.leaders$office.holder[i]," ")[[1]][1]
      }}
  #non-target countries
for(i in 1:nrow(other.leaders)){
  if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==8){
    other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][8]
    other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
    other.leaders$middle.name[i] <- paste(strsplit(other.leaders$office.holder[i]," ")[[1]][2],
                                          strsplit(other.leaders$office.holder[i]," ")[[1]][3],
                                          strsplit(other.leaders$office.holder[i]," ")[[1]][4],
                                          strsplit(other.leaders$office.holder[i]," ")[[1]][5],
                                          strsplit(other.leaders$office.holder[i]," ")[[1]][6],
                                          strsplit(other.leaders$office.holder[i]," ")[[1]][7])
    } else{
      if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==7){
        other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][7]
        other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
        other.leaders$middle.name[i] <- paste(strsplit(other.leaders$office.holder[i]," ")[[1]][2],
                                              strsplit(other.leaders$office.holder[i]," ")[[1]][3],
                                              strsplit(other.leaders$office.holder[i]," ")[[1]][4],
                                              strsplit(other.leaders$office.holder[i]," ")[[1]][5],
                                              strsplit(other.leaders$office.holder[i]," ")[[1]][6])
        } else{
          if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==6){
            other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][6]
            other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
            other.leaders$middle.name[i] <- paste(strsplit(other.leaders$office.holder[i]," ")[[1]][2],
                                                  strsplit(other.leaders$office.holder[i]," ")[[1]][3],
                                                  strsplit(other.leaders$office.holder[i]," ")[[1]][4],
                                                  strsplit(other.leaders$office.holder[i]," ")[[1]][5])
            } else{
              if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==5){
                other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][5]
                other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
                other.leaders$middle.name[i] <- paste(strsplit(other.leaders$office.holder[i]," ")[[1]][2],
                                                      strsplit(other.leaders$office.holder[i]," ")[[1]][3],
                                                      strsplit(other.leaders$office.holder[i]," ")[[1]][4])
                } else{
                  if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==4){
                    other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][4]
                    other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
                    other.leaders$middle.name[i] <- paste(strsplit(other.leaders$office.holder[i]," ")[[1]][2],
                                                          strsplit(other.leaders$office.holder[i]," ")[[1]][3])
                    } else{
                      if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==3){
                        other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][3] 
                        other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
                        other.leaders$middle.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][2]
                        } else{ 
                          if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==2){
                            other.leaders$last.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][2]
                            other.leaders$first.name[i] <- strsplit(other.leaders$office.holder[i]," ")[[1]][1]
                            other.leaders$middle.name[i] <- NA  
                            } else{ 
                          if(length(strsplit(other.leaders$office.holder[i]," ")[[1]])==0){
                            other.leaders$last.name[i] <- NA
                            other.leaders$first.name[i] <- NA
                            other.leaders$middle.name[i] <- NA  
                            }
                          }}}}}}}}
    
#isolate sideA actors
identified.leaders <- NULL
for(j in 1:nrow(rus.leaders)){
  if(str_detect(s,rus.leaders$last.name[j])){
    tagged.leaders <- filter(rus.leaders,rus.leaders$office.holder==as.character(rus.leaders$office.holder[j]))} else{next}
  identified.leaders <- rbind(identified.leaders,tagged.leaders)
  }
#couple sideA with relevant data
sideA.actor <- NULL
sideA.country <- NULL
sideA.actor.title <- NULL
for(i in 1:nrow(identified.leaders)){
  sideA.actor[i] <- as.character(identified.leaders$office.holder[i])
  sideA.country[i] <- as.character(identified.leaders$country[i])
  sideA.actor.title[i] <- as.character(identified.leaders$office[i])
  }

#isolate sideB actors #LEFT OFF HERE!!! 2.18.14
identified.leaders2 <- NULL

countrys <- other.leaders$country %>% as.character %>% unique 
for(k in 1:length(countrys)){
  temp <- other.leaders %>% filter(country==countrys[k])
  for(j in 1:nrow(temp)){
    if(!is.na(str_detect(s,temp$last.name[j])) & str_detect(s,temp$last.name[j])){
      tagged.leaders <- filter(other.leaders,other.leaders$office.holder==as.character(temp$office.holder[j]))} else{next}
    identified.leaders2 <- rbind(identified.leaders2,tagged.leaders)
    }
  tagged.leaders <- NULL
  }
identified.leaders2



for(j in 1:nrow(other.leaders)){
  
  if(str_detect(s,as.character(other.leaders$country[j]))){
    
    temp.sub.other.leaders <- other.leaders %>% filter(country==country[j])
    
    for(p in 1:nrow(temp.sub.other.leaders)){
      
      if(str_detect(s,temp.sub.other.leaders$last.name[p]) | str_detect(s,temp.sub.other.leaders$first.name[p])){
        tagged.leaders <- temp.sub.other.leaders %>% filter(as.character(temp.sub.other.leaders$office.holder)==as.character(temp.sub.other.leaders$office.holder[p])) 
        identified.leaders2 <- rbind(identified.leaders2,tagged.leaders)
        } else{next}
      
}  
} 
temp.sub.other.leaders <- NULL }

!is.na(str_detect(s,as.character(temp.sub.other.leaders$last.name[p]))) & 


#couple with relevant data re sideB actors
for(i in 1:nrow(identified.leaders2)){
  sideB.actor[i] <- as.character(identified.leaders2$office.holder[i])
  sideb.country[i] <- as.character(identified.leaders2$country[i])
  sideB.actor.title[i] <- as.character(identified.leaders2$office[i])
  }

#Data frame for this iteration
temp.data <- data.frame(sideA.actortitle=title,sideA.actor=sideA.actor,sideA.country=sideA.country)

```

### Text Correlations
```{r}
require(tm)
require(stringr)
#Material to test
corpus[[2]]$content
corpus[[2]]$meta[[3]] #This is a good test for names
brief <- corpus[[2]]$meta[[3]]

#Again, uploading the leader data
leader.data <- read.csv('Data/CIA_World_Leaders_Data_01.28.15.csv')

#Subset of just Russian Leaders
rus.leaders <- leader.data %>% filter(country=="Russia")
rus.leaders$office.holder <- as.character(rus.leaders$office.holder) %>% str_trim() %>% tolower()

side.A <- DocumentTermMatrix(as.String(brief) %>% VectorSource(.) %>% VCorpus,list(dictionary=rus.leaders$last.name))
for(i in 1:nrow(rus.leaders)){if(findFreqTerms(side.A, lowfreq=1)==rus.leaders$last.name[i]){test <- rus.leaders$office.holder[i]}}
test #Successful Extraction

#Let's try the other side. Here we need to subset by country

#Works if specify just FR
y <- other.leaders %>% filter(country=="France")
side.B <- DocumentTermMatrix(as.String(tolower(brief)) %>% VectorSource(.) %>% VCorpus,list(dictionary=y$last.name))
for(i in 1:nrow(y)){
  if(!is.na(y$last.name[i]) & findFreqTerms(side.B, lowfreq=1)==tolower(y$last.name[i])){
    test1 <- y$office.holder[i]}}
test1#Successful Extraction

#country detector
country <- other.leaders$country %>% unique %>% as.character %>% tolower()
c.identified <- DocumentTermMatrix(as.String(tolower(brief)) %>% VectorSource(.) %>% VCorpus,list(dictionary=country))
findFreqTerms(c.identified, lowfreq=1)


p <- other.leaders %>% filter(country=="Germany")
side.B <- DocumentTermMatrix(as.String(tolower(brief)) %>% VectorSource(.) %>% VCorpus,list(dictionary=p$last.name))
for(i in 1:nrow(p)){
  if(!is.na(p$last.name[i]) & findFreqTerms(side.B, lowfreq=1)==tolower(p$last.name[i])){
    test1 <- p$office.holder[i]}}
test1#Successful Extraction



side.A <- DocumentTermMatrix(as.String(brief) %>% VectorSource(.) %>% VCorpus,list(dictionary=str_split(rus.leaders$office.holder," ")))
for(i in 1:nrow(rus.leaders)){if(findFreqTerms(side.A, lowfreq=1)==rus.leaders$last.name[i]){test <- rus.leaders$office.holder[i]}}
test #Successful Extraction

DocumentTermMatrix(


findAssocs(DocumentTermMatrix(as.String(brief) %>% VectorSource(.) %>% VCorpus),scan_tokenizer(rus.leaders$last.name),.5)
```










