---
title: "rvest - Web Scrapping approach"
date: "January 19, 2015"
output: html_document
---
This is general walkthrough of implementing the `rvest` package to harvest data from the web. 

## the "rvest" package approach

`rvest` is a hadley package - play on "harvest". See [rvest - introduction](http://blog.rstudio.org/2014/11/24/rvest-easy-web-scraping-with-r/)

```{r}
require(rvest)
#For specifics on selector gadget to find the css of the website, see
#vignette("selectorgadget")

#To see capability, demo the package
#demo(package = "rvest")
require(dplyr) #for the pipe
```

Let's give it a swing pulling data similar to that of the vignette (i.e. IMDB movie data on the movie "Boyhood")
```{r}
boyhood.url <- html("http://www.imdb.com/title/tt1065073/fullcredits")
cast <- html_nodes(boyhood.url,"span.itemprop")
length(cast)
df <- html_text(cast) %>% data.frame(cast=.)
df$cast <- as.character(df$cast)
head(df)
#This has a list of all the actors in the movie
```

This was a simple exercise...though there are real limitations to this approach. One thing is that the selectorgadge can be a rather tedious thing to use. And even then you have to manually adapt it when you want to retrieve different pieces of information.

Here I will play with some of the versatility of the package
```{r,eval=F}
boyhood.url <- "http://www.imdb.com/title/tt1065073/"

#Here is a way to view html pages in Rstudio.
require(httpuv)
rstudio::viewer(boyhood.url)
#htm1_session(),jump_to(), follow_link(), back(), and forward()
html_session(boyhood.url) %>% follow_link("see full cast & crew")
```
